Paper \#ZW10157

### 2019-03-19 paper/submission/ZW10157-response-2.tex
small grammer and typo edits

{\bf Our response:} {\color{blue} This correction is in the new manuscript on line xxx.}

@@

{\bf Our response:} {\color{blue} This correction is in the new manuscript on line xxx.}

@@

{\bf Our response:} {\color{blue} This correction is in the new manuscript on line xxx.}

@@

III. D.

paragraph 1
The author's use of ``approach'' is ambiguous because it could be
interpreted as applying EA/GA multi-objective optimization to cavity
geometries since the emphasis of the paper is on providing a flexible
interface to EA/GAs or approach could mean the framework's software
design which is what, I think, they meant to convey. The authors
should make clear which ``approach'' they want the reader to consider.
A suggested change is:

@@

paragraph 1
the API in Listing 3 --> the API in Listing 2

paragraph 1
for those three --> for three

III. E.

paragraph 1
An expression parser --> an expression parser
(Note to authors: ``an expression parser'' is a continuation of the
sentence started before the code example introduced as an example.)

@@

IV.

paragraph 1
in Listing 3 --> in Listing 1

V. B. 2

paragraph 2
, and the to prevent --> and to prevent

@@

\vspace{1em}

That said, a general-purpose optimization system is a useful addition
to the design tools for accelerators. The way to entice prospective
users through PRAB is to introduce the system with a very brief
general overview and then focus on the results obtained using the
system. The detailed discussion of the design and implementation with
code snippets should be provided as Supplemental Material. PRAB is not
a computer journal. Salient implementation or design points if
necessary can be summarized in short Appendices; the main discussion
of the paper should be the optimization results not the details of the
implementation and design.

>>>>

{\bf Our response:} {\color{blue} This is corrected in the updated manuscript.}

@@

{\bf Our response:} {\color{blue} This grammar error is corrected in the updated manuscript.}

@@

{\bf Our response:} {\color{blue} This typo is corrected in the updated manuscript.}

@@

III. D. paragraph 1
The author's use of ``approach'' is ambiguous because it could be
interpreted as applying EA/GA multi-objective optimization to cavity
geometries since the emphasis of the paper is on providing a flexible
interface to EA/GAs or approach could mean the framework's software
design which is what, I think, they meant to convey. The authors
should make clear which ``approach'' they want the reader to consider.
A suggested change is:

@@

{\bf Our response:} {\color{blue} This suggestion was used on line xx.}

paragraph 1: the API in Listing 3 --$>$ the API in Listing 2

paragraph 1: for those three --$>$ for three

{\bf Our response:} {\color{blue} This was corrected in the updated manuscript.}

III. E. paragraph 1:
An expression parser --> an expression parser
(Note to authors: ``an expression parser'' is a continuation of the
sentence started before the code example introduced as an example.)

@@

IV. paragraph 1:
in Listing 3 --> in Listing 1

V. B. 2 paragraph 2:
, and the to prevent --> and to prevent

@@

\vspace{1em}
That said, a general-purpose optimization system is a useful addition
to the design tools for accelerators. The way to entice prospective
users through PRAB is to introduce the system with a very brief
general overview and then focus on the results obtained using the
system. The detailed discussion of the design and implementation with
code snippets should be provided as Supplemental Material. PRAB is not
a computer journal. Salient implementation or design points if
necessary can be summarized in short Appendices; the main discussion
of the paper should be the optimization results not the details of the
implementation and design.
